Time stability in human interaction networks, Supporting Information

### 2015-06-21 paper.tex
revisado SI
incorporadas revisoes e sugestoes do chu

Data from social networks used in this study were gathered and used within the Anthropological Physics principles~\cite{anPhy}.
All data used are also publicly accessible, either because they were already in public domain or because
we published our own annotations.
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participa.br was used from the linked data/semantic web RDF triples
reported in~\cite{opa} and available in~\cite{datahub}.

@@

\begin{table}
	\caption{Activity percentages of the months along the year from LAU list. Activity is concentrated in Jun-Aug for MET and LAD, and in Dec-Mar for CPP, LAU and LAD (see Section~\ref{si:months} of the Supporting Information). These observations fit academic calendars, vacations and end-of-year holidays.}
	\footnotesize
	\input{tables/tabMonthsLAU}
	\label{tab:min2}
\end{table}

>>>>

Data from social networks used in this study were gathered and used within the anthropological physics framework~\cite{anPhy}.
All data used are also publicly accessible, either because they were already in public domain or because
we published our own annotations.
Messages were downloaded from the GMANE public database~\cite{GMANEwikipedia}.
Data annotated from Facebook and Twitter are in a public repository~\cite{fbtwData}.
Data from Participa.br was used from the linked data/semantic web RDF triples
reported in~\cite{opa} and available in~\cite{datahub}.

@@

\begin{table}
	\caption{Activity percentages of the months along the year from LAU list. Activity is usually concentrated in Jun-Aug and/or in Dec-Mar (see Section~\ref{si:months} of the Supporting Information). These observations fit academic calendars, vacations and end-of-year holidays.}
	\footnotesize
	\input{tables/tabMonthsLAU}
	\label{tab:min2}
\end{table}

### 2015-06-21 supportingInformation.tex
incorporadas revisoes e sugestoes do chu

\section{Time activity in different scales}\label{sec:time}
Theory presented in Section~\ref{sec:mtime} and results in Section~\ref{constDisc} of the paper~\cite{tpaper}.

\subsection{Time circular measures}\label{si:circ}
The rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence $\frac{max(incidence)}{min(incidence)}$ at each time unit.
Also, $ \mu_{\frac{max(incidence')}{min(incidence')}} $ and $ \sigma_{\frac{max(incidence')}{min(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples. Greater dispersion is found on seconds and minutes, followed
by days of the month. Greater localization if found in the hours of the day, followed by weekdays and months.

@@

Activity percentages along the hours of the day. Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight. Around 2/3 of the whole activity takes place from noon to midnight. Nevertheless, the activity peak occurs around midday, with a slight skew toward one hour before noon.
\begin{table}[!h]
	\caption{LAU activity along the hours of the day.}
	\footnotesize
	\input{tables/tabHoursLAU}
\end{table}

@@

\FloatBarrier
\subsubsection{Histograms of activity along the days of the week}

Activity percentages along the days of the week. Higher activity was observed during weekdays, with a decrease of activity on weekends of at least one third and two thirds in extreme cases.

@@

\FloatBarrier
\subsubsection{Histograms of activity along the days of the month}\label{si:monthdays}
Although slightly higher activity rates are found in the beginning of the month, the most important feature seems to be the homogeneity made explicit by the high circular dispersion in the tables of Section~\ref{si:circ}.
\begin{table}[!h]
	\caption{LAU activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysLAU}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{LAD activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysLAD}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{MET activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysMET}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{CPP activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysCPP}
\label{tab:min}
\end{table}

\FloatBarrier
\subsubsection{Histograms of activity along months of the year}\label{si:months}
	Activity percentages in the months along the year.
	Activity is concentrated in Jun-Aug for MET and LAD, and in Dec-Mar for CPP, LAU and LAD.
	These observations fit academic calendars, vacations and end-of-year holidays.

\begin{table}[!h]
	\caption{LAU activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsLAU}
\label{tab:min2}
\end{table}
\begin{table}[!h]
	\caption{LAD activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsLAD}
\label{tab:min2}
\end{table}
\begin{table}[!h]
	\caption{MET activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsMET}
\label{tab:min2}
\end{table}

@@

\FloatBarrier
\section{PCA of measures along the timeline}\label{si:pcat}
Loadings for the 14 metrics into the principal components are given for all LAD, LAU, MET, CPP, lists, $ws=1000$ messages in 20 disjoint positioning.
The clustering coefficient (cc) appears as the first metric in the tables, followed by 7 centrality metrics and 6 symmetry-related metrics.
Note that the centrality metrics, including degrees, strength and betweenness centrality, are the most important contributors for the first principal component, while the second component is dominated by symmetry metrics.
The clustering coefficient is only relevant for the third principal component, coupled with standard deviations of strengths and degrees.
The three components have in average 80.36\% of the variance.
Further details are given in Sections~\ref{measures} and~\ref{prevalence} of the main document~\cite{tpaper}.

>>>>

\section{Time activity in different scales}\label{sec:time}
Here we complement the theory presented in Section~\ref{sec:mtime} and results in Section~\ref{constDisc} of the paper~\cite{tpaper}.

\subsection{Time circular measures}\label{si:circ}
The measurements used were were the rescaled circular mean $\theta_\mu'$, standard deviation $S(z)$, variance $Var(z)$, circular dispersion $\delta(z)$ and the relation of maximum and minimum incidence $\frac{max(incidence)}{min(incidence)}$ at each time unit.
Also, $ \mu_{\frac{max(incidence')}{min(incidence')}} $ and $ \sigma_{\frac{max(incidence')}{min(incidence')} }$ are given for 1000 uniform distribution simulations within the same number of bins and with the same number of samples. Greater dispersion is found on seconds and minutes, followed
by days of the month. Greater localization if found in the hours of the day, followed by weekdays and months.

@@

Higher activity was observed between noon and 6pm, followed by the time period between 6pm and midnight.
Around 2/3 of the whole activity takes place from noon to midnight.
The activity peak occurs around midday, with a slight skew toward one hour before noon.
\begin{table}[!h]
	\caption{LAU activity along the hours of the day.}
	\footnotesize
	\input{tables/tabHoursLAU}
\end{table}

@@

\FloatBarrier

\subsubsection{Histograms of activity along the days of the week}
Most notably, a decrease of activity on weekends of at least one third and at most two thirds.

@@

\FloatBarrier
\subsubsection{Histograms of activity along the days of the month}\label{si:monthdays}
The most important feature seems to be the homogeneity made explicit by the high circular dispersion in the tables of Section~\ref{si:circ}. Slightly higher activity rates are found in the beginning of the month, although not statistically significant.
\begin{table}[!h]
	\caption{LAU activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysLAU}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{LAD activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysLAD}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{MET activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysMET}
\label{tab:min}
\end{table}
\begin{table}[!h]
	\caption{CPP activity along the days of the month.}
	\footnotesize
	\input{tables/tabMonthdaysCPP}
\label{tab:min}
\end{table}

\FloatBarrier
\subsubsection{Histograms of activity along months of the year}\label{si:months}
	Activity is concentrated in Jun-Aug and/or in Dec-Mar.
	These observations mostly fit academic calendars, vacations and end-of-year holidays.
\begin{table}[!h]
	\caption{LAU activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsLAU}
\label{tab:min2}
\end{table}
\begin{table}[!h]
	\caption{LAD activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsLAD}
\label{tab:min2}
\end{table}
\begin{table}[!h]
	\caption{MET activity along the months of the year.}
	\footnotesize
	\input{tables/tabMonthsMET}
\label{tab:min2}
\end{table}

@@

\FloatBarrier
\section{PCA of measures along the timeline}\label{si:pcat}
Loadings for the 14 metrics into the principal components are given for all LAD, LAU, MET, CPP, lists, $ws=1000$ messages in 20 disjoint positioning.
The clustering coefficient (cc) appears as the first metric in the tables, followed by 7 centrality metrics and 6 symmetry-related metrics.
The centrality metrics, including degrees, strength and betweenness centrality, are the most important contributors for the first principal component, while the second component is dominated by symmetry metrics.
The clustering coefficient is only relevant for the third principal component, coupled with standard deviations of strengths and degrees.
The three components have in average 80.36\% of the variance.
Further details are given in Sections~\ref{measures} and~\ref{prevalence} of the main document~\cite{tpaper}.
